# Testing text output

See if chunk options like `tidy`, `prompt` and `echo`, etc work as expected.

## A normal chunk

```{r demo}
1+1
for (i in 1:10) {
# nothing
}
# two blank lines below


dnorm(0)
```

## Do not evaluate

```{r demo, eval=FALSE}
```

## Add prompts

```{r demo, prompt=TRUE}
```

## No evaluate or tidy

```{r demo, prompt=TRUE, eval=FALSE}
```

## Do not tidy

```{r demo, tidy=FALSE}
```

## Do not echo

```{r demo, echo=FALSE}
```

## Do not comment out results

```{r demo, comment=NA}
```

## Do not echo the 2nd expression

```{r demo, echo=-2}
```

## Only evaluate the first two expressions

```{r demo, eval=1:2}
```

## Add prompts but no tidy

```{r demo, tidy=FALSE, prompt=TRUE}
```

## Change prompts

```{r}
options(prompt='R> ', continue='+  ')
```

```{r demo, prompt=TRUE}
```

## Backslashes

```{r}
{
# can you deal with \code{foo} or \n, \a?
gsub('\\.', '\\\\', 'a.b.c') # \link{bar}
}
cat('a\tb\nc')
```

## Other formatR options

```{r}
options(keep.blank.line=FALSE)
```

```{r demo, eval=FALSE}
```

```{r}
options(keep.comment=FALSE)
```

```{r demo, eval=FALSE}
```

```{r}
options(left.brace.newline=TRUE, keep.comment=TRUE)
```

```{r demo, echo=2}
```

See <http://yihui.name/formatR> for details.

## Empty chunks

```{r}

```
