R works, of course.

``` {r test-r, engine='R'}
set.seed(123)
rnorm(5)
```

Does **knitr** work with Python? Use the chunk option `engine='python'`:

```{r test-python, engine='python'}
x = 'hello, python world!'
print x
print x.split(' ')
```

## Chunk Options

You can use some chunk options like `eval`, `echo` and `results`. For example, `eval=FALSE` (do not evaluate code):

```{r test-eval, engine='python', eval=FALSE, ref.label='test-python'}
```

or `echo=FALSE` (hide source code):

```{r test-echo, engine='python', echo=FALSE, ref.label='test-python'}
```

or `results='hide'`:

```{r test-hide, engine='python', results='hide', ref.label='test-python'}
```

or `results='asis'`:

```{r test-asis, engine='python', results='asis'}
print '**Write** _something_ in `Markdown` from `Python`!'
```

You can also cache the computation:

```{r test-cache, engine='python', cache=TRUE}
import time
# pretend this is a time-consuming task...
time.sleep(10)
print 1+1
```

## Strict Markdown

You can use strict markdown (i.e. indent by 4 spaces) by setting `render_markdown(TRUE)`.

```{r strict-markdown}
render_markdown(TRUE)
```

Now see how the output is changed:

```{r test-py-again, ref.label='test-python', engine='python'}
```
