# Call Rcpp from knitr

```{r setup, include=FALSE}
opts_chunk$set(cache = TRUE) # because the compilation takes time, let's cache it
```

When the chunk option `engine='Rcpp'` is specified, the code chunk will be compiled through **Rcpp** via `cppFunction()` or `sourceCpp()` (the latter is called if an `Rcpp::export` attribute was detected in the code chunk).

Test for `fibonacci`:

```{r fibCpp, engine='Rcpp'}
int fibonacci(const int x) {
    if (x == 0 || x == 1) return(x);
    return (fibonacci(x - 1)) + fibonacci(x - 2);
}
```

It can be called as a normal R function now:

```{r fibTest, dependson='fibCpp'}
fibonacci(10L)
fibonacci(20L)
```

The above example defines a single C++ function by calling `cppFunction()`(which automatically includes the `<Rcpp.h>` header). If you want to define multiple functions (or helper functions that are not exported) then you need to add the appropriate includes and `Rcpp::export` attributes. For example:

```{r multipleCpp, engine='Rcpp'}
#include <Rcpp.h>

using namespace Rcpp;

// [[Rcpp::export]]
NumericVector convolveCpp(NumericVector a, NumericVector b) {
  
    int na = a.size(), nb = b.size();
    int nab = na + nb - 1;
    NumericVector xab(nab);
    
    for (int i = 0; i < na; i++)
        for (int j = 0; j < nb; j++)
            xab[i + j] += a[i] * b[j];
    
    return xab;
}

// [[Rcpp::export]]
List lapplyCpp(List input, Function f) {
    
    List output(input.size());
    
    std::transform(input.begin(), input.end(), output.begin(), f);
    output.names() = input.names();
    
    return output;
}
```

If you want to link to code defined in another package (e.g **RcppArmadillo**) then you need to provide an `Rcpp::depends` attribute. For example:

```{r lmCpp, engine='Rcpp'}
// [[Rcpp::depends(RcppArmadillo)]]

#include <RcppArmadillo.h>

using namespace Rcpp;

// [[Rcpp::export]]
List fastLm(NumericVector yr, NumericMatrix Xr) {

    int n = Xr.nrow(), k = Xr.ncol();

    arma::mat X(Xr.begin(), n, k, false); // reuses memory and avoids extra copy
    arma::colvec y(yr.begin(), yr.size(), false);

    arma::colvec coef = arma::solve(X, y);      // fit model y ~ X
    arma::colvec resid = y - X*coef;            // residuals

    double sig2 = arma::as_scalar( arma::trans(resid)*resid/(n-k) );
                                                // std.error of estimate
    arma::colvec stderrest = arma::sqrt(
                    sig2 * arma::diagvec( arma::inv(arma::trans(X)*X)) );

    return List::create(Named("coefficients") = coef,
                        Named("stderr")       = stderrest
    );
}
```

A test:

```{r lmTest}
fastLm(rnorm(10), matrix(1:20, ncol = 2))
```

Finally, you can combine the simpler syntactic form of defining a single function with the use of an external package by specifying a plugin using `engine.opts`. For example, here we use the **RcppArmadillo** package via a plugin:

<code>
&#96;&#96;&#96;{r lmCpp2, engine.opts=list(plugin='RcppArmadillo')}
</code>
```{r lmCpp2, engine='Rcpp', engine.opts=list(plugin='RcppArmadillo')}
List fastLm2(NumericVector yr, NumericMatrix Xr) {

    int n = Xr.nrow(), k = Xr.ncol();

    arma::mat X(Xr.begin(), n, k, false); // reuses memory and avoids extra copy
    arma::colvec y(yr.begin(), yr.size(), false);

    arma::colvec coef = arma::solve(X, y); // fit model y ~ X
    arma::colvec resid = y - X*coef; // residuals

    double sig2 = arma::as_scalar( arma::trans(resid)*resid/(n-k) );
                                                // std.error of estimate
    arma::colvec stderrest = arma::sqrt(
                    sig2 * arma::diagvec( arma::inv(arma::trans(X)*X)) );

    return List::create(Named("coefficients") = coef,
                        Named("stderr") = stderrest
    );
}
```
&#96;&#96;&#96;
