# Three arguments in chunk hooks

A chunk hook has three arguments: `before`, `options` and `envir`. We show how they work through some simple examples.

## The `before` argument

It is a logical argument: `before == TRUE` executes code before a chunk.

```{r}
knit_hooks$set(foo1 = function(before, options, envir) {
  if (before) {
    '_I appear before a chunk!_\n\n'
  } else {
    '\n\n_I am after a chunk..._'
  }
})
```

Test the `foo1` hook:

```{r foo1='whatever'}
1+1
```

## The `options` argument

It contains all the chunk options (include global options) for the current chunk.

```{r}
knit_hooks$set(foo2 = function(before, options, envir) {
  if (!before) {
    z = capture.output(str(options[c('eval', 'dev', 'results', 'bar1', 'bar2', 'bar3')]))
    z = paste('    ', z, sep = '', collapse = '\n')
    paste('Some chunk options in the above chunk are:\n\n', z, sep = '')
  }
})
```

Test the `foo2` hook:

```{r foo2='hi', bar1=TRUE, bar2='asdf', bar3=3.14159}
1+1
```

## The `envir` argument

It is the environment of the current chunk.

```{r}
knit_hooks$set(foo3 = function(before, options, envir) {
  if (!before) {
    paste('Objects available in the above chunk:',
          paste('`', ls(envir), '`', sep = '', collapse = ', '))
  }
})
```

Test the `foo3` hook:

```{r foo3=TRUE}
x2=1+1; y3=rnorm(10)
```

Another example:

```{r}
knit_hooks$set(foo4 = function(before, options, envir) {
  if (!before && exists('z5', envir = envir)) {
    sprintf('**Ha! I see z5 = %.3f!**', envir$z5)
  }
})
```

Test `foo4`:

```{r foo4='qwer'}
pi
```

This above chunk is quiet because `z5` does not exist yet.

```{r foo4='asdf'}
z5=2*pi
```
