---
title: "Tikz with svg output"
output: html_document
---

```{r}
library(knitr)
## convert tikz string to PDF
`%n%` = function(x, y) if (is.null(x)) y else x
eng_svgtikz = function(options) {
  if (!options$eval) return(engine_output(options, options$code, ''))

  lines = readLines(tmpl <- options$engine.opts$template %n%
                      system.file('misc', 'tikz2pdf.tex', package = 'knitr'))
  i = grep('%% TIKZ_CODE %%', lines)
  if (length(i) != 1L)
    stop("Couldn't find replacement string; or the are multiple of them.")

  s = append(lines, options$code, i)  # insert tikz into tex-template
  writeLines(s, texf <- paste0(f <- tempfile('tikz', '.'), '.tex'))
  on.exit(unlink(texf), add = TRUE)
  unlink(outf <- paste0(f, '.dvi'))
  tools::texi2dvi(texf, pdf=F, clean = T)
  if (!file.exists(outf)) stop('failed to compile tikz; check the template: ', tmpl)
  
  fig = fig_path('', options)
  dir.create(dirname(fig), recursive = TRUE, showWarnings = FALSE)
  file.rename(outf, paste0(fig, '.dvi'))
   
  # dvisvgm needs to be on the path
  # dvisvgm for windows needs ghostscript bin dir on the path also
  conv = system2("dvisvgm", sprintf("%s.dvi", fig))
  if (conv != 0 && !options$error)
    stop('problems with `dvisvgm`; probably not installed?')
  
  # copy the svf to figure-html subdir
  file.rename(paste0(basename(fig),".svg"), paste0(fig,".svg"))
  
  options$fig.num = 1L; options$fig.cur = 1L
  extra = knit_hooks$get('plot')(paste(fig, "svg", sep = '.'), options)
  options$engine = 'tex'  # for output hooks to use the correct language class
  engine_output(options, options$code, '', extra)
}

knit_engines$set(svgtikz = eng_svgtikz)
```


# TikZ graphics

## Description

The engine inserts the code into a latex-string-template, which is then processed by LaTeX (and ImageMagick `convert` if `fig.ext` is not `pdf`).

## Options

You can pass some options to the engine by defining `engine.opts`, e.g. use your own template instead of the default one to include the tikz code: `engine.opts = list(template = "mytemplate.tex")`. The default template can be found under `system.file('misc', 'tikz2pdf.tex', package = 'knitr')`.

## Example

An example of the tikz-engine from <https://raw.github.com/sdiehl/cats/master/misc/example.md>

```{r tikz-ex, engine = "svgtikz", fig.cap = "Funky tikz", fig.ext = 'png', cache=TRUE}
\usetikzlibrary{arrows}
\begin{tikzpicture}[node distance=2cm, auto,>=latex', thick, scale = 0.1]
\node (P) {$P$};
\node (B) [right of=P] {$B$};
\node (A) [below of=P] {$A$};
\node (C) [below of=B] {$C$};
\node (P1) [node distance=1.4cm, left of=P, above of=P] {$\hat{P}$};
\draw[->] (P) to node {$f$} (B);
\draw[->] (P) to node [swap] {$g$} (A);
\draw[->] (A) to node [swap] {$f$} (C);
\draw[->] (B) to node {$g$} (C);
\draw[->, bend right] (P1) to node [swap] {$\hat{g}$} (A);
\draw[->, bend left] (P1) to node {$\hat{f}$} (B);
\draw[->, dashed] (P1) to node {$k$} (P);
\end{tikzpicture}
```

## Tips

To develop the tikz-code, you could use `qtikz` or `ktikz`.
