# Wrap long lines
 
Long lines in the output will not be (hard-)wrapped automatically unless you break them manually.

```{r long_output}
a <- '## "stx2A; shiga-like toxin II A subunit encoded by bacteriophage BP-933W; K11006 shiga toxin subunit A" '
a
```

Perhaps you see it is wrapped in RStudio, but that is because `<pre>` has the CSS attribute `white-space: pre-wrap;`. For LaTeX output, the output is in the `verbatim` environment by default, which will not wrap long lines (everything is shown as is).

You can redefine the output hook function so that you can instruct some chunks to hard-wrap their output lines, e.g.

```{r wrap-hook}
hook_output = knit_hooks$get('output')
knit_hooks$set(output = function(x, options) {
  # this hook is used only when the linewidth option is not NULL
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    # any lines wider than n should be wrapped
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  hook_output(x, options)
})
```

Now see the output of `a` (note `linewidth` is not a default **knitr** option):

```{r test, linewidth=60}
a
```
