% Converting Markdown to Other Formats with knitr::pandoc()
% [Yihui Xie](http://yihui.name)
% March 1st, 2013

<!--pandoc
t: html
s:
mathjax:
number-sections:

t: latex
number-sections:
-->

A bit _introduction_ here.

# Start with a cool section

You can use traditional **Markdown** syntax, such as [links](http://yihui.name/knitr) and `code`.

# Followed by another section

Of course you can write lists:

- apple
- pear
- banana

Or ordered lists:

1. items
1. will
1. be
1. ordered
    - nested
    - items

# More sections

## Hi

hi hi

## Hello

hello hello

## Howdy

howdy howdy

# Okay, some R code

```{r linear-model}
fit = lm(dist ~ speed, data = cars)
b = coef(fit)  # coefficients
summary(fit)
```

The code will be highlighted in all output formats.

# And some pictures

```{r lm-vis, fig.cap='Regression diagnostics'}
par(mfrow = c(2, 2), pch = 20, mar = c(4, 4, 2, .1), bg = 'white')
plot(fit)
```

# A little bit math

Our regression equation is $Y=`r b[1]`+`r b[2]`x$, and the model is:

$$ Y = \beta_0 + \beta_1 x + \epsilon$$

