# Asymptote graphics example

## Description

The engine runs the code using the `asy` command line program. The result can be `svg`, `png` or `pdf`. `svg` renders better within html. For latex `pdf` should be used.

see [Asymptote website](http://asymptote.sourceforge.net/) for installation and documentation.

On osx, one can simply run:

    brew install asymptote
    
Please have a look at the online [gallery](http://asymptote.sourceforge.net/gallery/index.html) to see how much can be done with asymptote. 

## Example

An example of the asy-engine:


```{r asy-simple-ex, engine = "asy", fig.cap = "Asymptote Example", fig.ext = 'svg', cache=FALSE}
real u = 40;
// just a comment
draw( (0,0) .. (u,u) .. (u,0) -- (0,0) );
```


## 3D example


```{r asy-3d-ex, engine = "asy", fig.cap = "Asymptote 3D Example", fig.ext = 'png', cache=FALSE}
import graph3;
import palette;
       
size(200,300,keepAspect=false);
//settings.nothin=true;
       
currentprojection=orthographic(10,10,30);
currentlight=(10,10,5);
triple f(pair t) {return (exp(t.x)*cos(t.y),exp(t.x)*sin(t.y),t.y);}
       
surface s=surface(f,(-4,-2pi),(0,4pi),8,16,Spline);
s.colors(palette(s.map(zpart),Rainbow()));
draw(s,render(merge=true));
```



