# Asymptote graphics example

## Description

The engine runs the code using the `asy` command line program. The result can be `svg`, `png` or `pdf`. `svg` renders better within html. For latex `pdf` should be used.

see [Asymptote website](http://asymptote.sourceforge.net/) for installation and documentation.

On osx, one can simply run:

    brew install asymptote
    
Please have a look at the online [gallery](http://asymptote.sourceforge.net/gallery/index.html) to see how much can be done with asymptote. 

## Example

In this example, I  generate data in R and then use it for plotting in asymptote. In addition I use asymptote to find the intersection between the R path and a line. At that intersection I add a latex label.

```{r}
x = seq(0,5,l=100)
y = sin(x)

# save data to csv file
write.table(data.frame(x,y),file='asy.csv',col.names=FALSE,row.names=FALSE,sep=',')
```

```{r asy-ex, engine = "asy", fig.cap = "Asymptote Example", fig.ext = 'svg', cache=FALSE}
import graph;
size(200,150,IgnoreAspect);

// import data from csv file
file in=input("asy.csv").line().csv();
real[][] a=in.dimension(0,0);
a=transpose(a);

// generate a path
path rpath = graph(a[0],a[1]);
path lpath = (1,0)--(5,1);

// find intersection
pair pA=intersectionpoint(rpath,lpath);

// draw all
draw(rpath,red);
draw(lpath,dashed + blue);
dot("$\delta$",pA,NE);
xaxis("$x$",BottomTop,LeftTicks);
yaxis("$y$",LeftRight,RightTicks);
```






