# Embed animations using SciAnimator in knitr

We can set the package option `animation.fun` to `hook_scianimator` so that
multiple plots in a chunk can be animated via the SciAnimator library.

```{r setup}
library(knitr)
opts_knit$set(animation.fun = hook_scianimator)
```

You have to embed the jQuery and SciAnimator libraries in the HTML header
(between `<head>` and `</head>`), even though some browsers can tolerate it
if you insert a style sheet after `<body>`.

<link rel="stylesheet" href="http://vis.supstat.com//assets/themes/dinky/css/scianimator.css">
<script src="https://ajax.googleapis.com/ajax/libs/jquery/1.7.1/jquery.min.js"></script>
<script src="http://vis.supstat.com/assets/themes/dinky/js/jquery.scianimator.min.js"></script>

Here comes a test of the Brownian motion:

```{r test, fig.show='animate', interval=.1}
n = length(palette())
x = rnorm(n); y = rnorm(n)
for (i in 1:20) {
  x = x + rnorm(n); y = y + rnorm(n)
  plot(x, y, xlim=c(-10, 10), ylim=c(-10,10), pch=19, col=1:n, cex=2)
}
```

There are many other examples at <http://vis.supstat.com>.
