---
title: "HTML-Class Demo"
author: "Ian Lyttle"
---

Here are some (newer) options you can use with **knitr**, `class.source` and `class.output`. Both are useful only for rendering R Markdown files into HTML. Multiple classes can be set by providing a vector, or a space-delimited string, i.e. `class.source = c("foo", "bar")` or `class.source = "foo bar"`.

One way this can be useful is motivated by the original [Stack Overflow question](http://stackoverflow.com/q/41030477/559676), how can we use **knitr** to help us to emphasize "bad" coding practices?

## Using Bootstrap

Using R Markdown, the default behavior is to include the Bootstrap framework. This can make things very easy for you to signify your code and your output. Bootstrap defines some [CSS classes for backgrounds](http://getbootstrap.com/css/#helper-classes-backgrounds): `"bg-primary"`, `"bg-success"`, `"bg-info"`, `"bg-warning"`, and `"bg-danger"`.

For example, we are warned that the normal subsetting of a data frame can be type-unstable. To show this here,  the chunk options are set: `class.source = 'bg-warning', class.output = 'bg-warning'`.

```{r df-drop, class.source='bg-warning', class.output='bg-warning'}
mtcars[, "mpg"]
```

To make sure that we return a data frame, we set the argument `drop = FALSE`. Here the chunk options are set: `class.source = 'bg-success', class.output = 'bg-success'`.

```{r df-drop-ok, class.source='bg-success', class.output='bg-success'}
mtcars[, "mpg", drop=FALSE]
```

## Using custom css

You may wish to set your own CSS -- **knitr** and **rmarkdown** make this easy for you. If you are using the **rmarkdown** package, you can include your CSS file by setting a parameter in the YAML header ([reference](http://rmarkdown.rstudio.com/html_document_format.html#custom_css)). You can also include a chunk of CSS code, as is done here.

Note that for this example, only `class.source` is set.

```{css}
.bad-code { background-color: salmon; }
```

```{r df-drop-2, class.source='bad-code'}
mtcars[, "mpg"] 
```
