---
title: "Test ref.label and opts.label"
---

## Chunk a

```{r, a, echo=FALSE, comment='#> '}
1 + 1
2 + 2
```

## Chunk b

```{r, b, results='hide'}
1:10
```

## Setting `opts_template`

```{r}
knitr::opts_template$set(
  skip = list(eval = FALSE),
  b = list(results = 'markup', prompt = TRUE)
)
```

## `ref.label = 'a'`

Ignore chunk options on chunk `a`:

```{r, ref.label='a'}
```

## `ref.label = I('a')`

Inherit chunk options from chunk `a`:

```{r, ref.label=I('a')}
```

## `ref.label = 'a'` and `opts.label = TRUE`

Inherit chunk options from chunk `a`:

```{r, ref.label='a', opts.label='a'}
```

## `ref.label = 'a'` and `opts.label = 'b'`

Inherit chunk options from template `b` and then chunk `b`:

```{r, ref.label='a', opts.label='b'}
```

## `ref.label = c('b', 'a')` and `opts.label = TRUE`

Inherit chunk options from chunk `b` (no output) and `a` (no source), so you see nothing below:

```{r, ref.label=c('b', 'a'), opts.label=TRUE}
```

## `ref.label = I(c('b', 'a'))`

Same as the previous section---you see nothing below:

```{r, ref.label=I(c('b', 'a'))}
```

## `ref.label = I(c('b', 'a'))` and `echo = TRUE`

Inherit chunk options from chunk `b` (no output) and `a` (no source), and then override with `echo = TRUE`:

```{r, ref.label=c('b', 'a'), opts.label=TRUE, echo=TRUE}
```

## `ref.label = c('b', 'a')` and `opts.label = 'a'`

Inherit code from chunk `b` and `a`, and chunk options from chunk `a` (no source):

```{r, ref.label=c('b', 'a'), opts.label='a'}
```

## `ref.label = c('b', 'a')` and `opts.label = 'skip'`

Inherit code from chunk `b` and `a`, and chunk options from template `skip` (no evaluation):

```{r, ref.label=c('b', 'a'), opts.label='skip'}
```

## `ref.label = I(c('b', 'a'))` and `opts.label = 'skip'`

Inherit code from chunk `b` and `a`, and chunk options from template `skip` (ignore `I()` in `ref.label` since `opts.label` is not empty):

```{r, ref.label=I(c('b', 'a')), opts.label='skip'}
```
